The LSST-DESC 3x2pt Tomography Optimization Challenge

### 2021-09-27 paper/paper.tex
more tweaks

Various recent work have explored general tomographic binning strategies. The general question of optimization
was recently discussed in detail
in \citet{rainbow} using a self-organizing map (SOM) approach to target up to five tomographic bins.  For this
configuration they find that equally spaced redshift bins are a good proxy
for an optimized method, but note, importantly, that we should not be constrained to trying to directly
match our bin selections to specific tomographic bin edges. 
They also highlight the utility of rejecting outlier or hard-to-classify objects from samples, and the ability of SOMs
to do so cleanly.
\citet{taylor18} considered using
fine tomographic bins as an alternative to fully 3D lensing, and found that the strategy of equal numbers
per bin is less effective at high redshift, a result we will echo in this paper. The fine-binning strategy
also allows a set of nulling methods to be applied, offering various advantages in avoiding poorly-understood
regimes \citep{taylor18b,bnt,xcut}.
Most recently, \citet{euclid-nz} studied this question with respect to the Euclid mission, using the \textit{Flagship}
simulation and applying realistic photometric redshift estimation methods to the
sample (we defer this question in this work). They highlight the power of using large numbers of bins,
differences in ideal binnings when
changing the choice of data (the inclusion galaxy galaxy-lensing), and
note the value in discarding galaxies with high redshift uncertainty. We will echo many of these issues below.

@@

\begin{figure*}
\includegraphics[width=1\linewidth]{results/metric_grid_dc2_griz.pdf}
\caption{Normalized scores for each method, normalized between the score for random assignment (zero) and truth assignment to bins with equal number counts (one).  It can be seen that both equal-number and equal-redshift spacings can be beaten for certain metrics.  In each case, classification is done using griz bands on the CosmoDC2 data set; equivalent plots for Buzzard and riz are shown in \autoref{app:metric_grids}.
\emph{ww} indicates lensing-only metrics, \emph{gg} indicates clustering only, and \emph{3x2pt} their combination.
The three metrics are defined in \autoref{sec:metrics}.
}
\label{fig:metric_grid_dc2_griz}
\end{figure*}

@@

This model does not include a number of theoretical effects that will be important in real data, including
intrinsic alignments, non-Gaussian covariance, and a range of effects on spectra at small scales, like non-linear 
bias and beyond-Limber effects. Collectively these effects mean that our tests are exaggerating the constraining
power of small-scale signals, and increasing all our metrics (especially as our $\ell$ range is fixed with $z$).  
Although this unrealistic aspect mostly affects algorithms equally, the relation between redshift, angle, and physical scale means that the exaggeration is especially strong for low redshift, and so it
could plausibly favour methods that are better in that range.

@@

These method were submitted by the author AP.
They used optimized bin edges.

>>>>

Various recent work have explored general tomographic binning strategies. The general question of optimization
was recently discussed in detail
in \citet{rainbow} using a self-organizing map (SOM) approach to target up to five tomographic bins.  For this
configuration they find that equally spaced redshift bins are a good proxy
for an optimized method, but note, importantly, that we should not be constrained to trying to directly
match our bin selections to specific tomographic bin edges. 
They also highlight the utility of rejecting outlier or hard-to-classify objects from samples, and the ability of SOMs
to do so cleanly.
\citet{taylor18} considered using
fine tomographic bins as an alternative to fully 3D lensing, and found that the strategy of equal numbers
per bin is less effective at high redshift, a result we will echo in this paper. The fine-binning strategy
also allows a set of nulling methods to be applied, offering various advantages in avoiding poorly-understood
regimes \citep{taylor18b,bnt,xcut}.
Most recently, \citet{euclid-nz} studied this question with respect to the Euclid mission, using the \textit{Flagship}
simulation and applying realistic photometric redshift estimation methods to the
sample (we defer the latter in this work). They highlight the power of using large numbers of bins,
differences in ideal binnings when
changing the choice of data (the inclusion galaxy galaxy-lensing), and
note the value in discarding galaxies with high redshift uncertainty. We will echo many of these issues below.

@@

\begin{figure*}
\includegraphics[width=1\linewidth]{results/metric_grid_dc2_griz.pdf}
\caption{Normalized scores for each method, normalized between the score for random assignment (zero) and truth assignment to bins with equal number counts (one).  It can be seen that both equal-number and equal-redshift spacings can be beaten for certain metrics.  In each case, classification is done using griz bands on the CosmoDC2 data set; equivalent plots for Buzzard and riz are shown in \autoref{app:metric_grids}.
\emph{ww} indicates lensing-only metrics, \emph{gg} indicates clustering only, and \emph{3x2} their combination.
The three metrics are defined in \autoref{sec:metrics}.
}
\label{fig:metric_grid_dc2_griz}
\end{figure*}

@@

This model does not include a number of theoretical effects that will be important in real data, including
intrinsic alignments, non-Gaussian covariance, and a range of effects on spectra at small scales, like non-linear 
bias and beyond-Limber effects. Collectively these effects mean that our tests are exaggerating the constraining
power of small-scale signals, and increasing all our metrics (especially as our $\ell$ range is fixed with $z$).  
Although this unrealistic aspect mostly affects algorithms equally, the relation between redshift, angle, and physical scale means that the exaggeration is especially strong for low redshift, and so it
could plausibly favour methods that create narrower bins in that range.

@@

These methods were submitted by the author AP.
They used optimized bin edges.
